Twisted \(M\)-theory and its perturbative quantization.

### 2020-11-24 paper.tex
merge

There is a component $\mu_{Q\Bar{Q}}^{1,1}$ of $\mu^{1,1}$ which is a Beltrami differential for the quotient bundle $Q$.
At the level of the quotient bundle Equation (\ref{eqn:mu11}) becomes
\[
  \dbar \mu^{1,1}_{Q \Bar{Q}} + \frac12 \{\mu^{1,1}_{Q \Bar{Q}} , \mu^{1,1}_{Q \Bar{Q}}\}_{\rm NS} = 0 .
\]
In other words $\mu^{1,1}_F$ is a Beltrami differential for this quotient bundle and hence determines a deformation of complex structure of $T^{1,0}_X / F$.

>>>>

There is a component $\mu_{Q\Bar{Q}}^{1,1}$ of $\mu^{1,1}$ which is a Beltrami differential for the quotient bundle $Q$.
At the level of the quotient bundle Equation (\ref{eqn:mu11}) becomes
\[
  \dbar \mu^{1,1}_{Q \Bar{Q}} + \frac12 \{\mu^{1,1}_{Q \Bar{Q}} , \mu^{1,1}_{Q \Bar{Q}}\}_{\rm NS} = 0 .
\]
In other words $\mu^{1,1}_{Q \Bar{Q}}$ is a Beltrami differential for this quotient bundle and hence determines a deformation of complex structure of $Q = T^{1,0}_X / F$.

So, after fixing the value of $\beta \partial \gamma^{1,0}$.
The remaining components of $\mu^{1,1}$ determine deformations of complex structure of the bundle $F \subset T^{1,0}_X$.
For instance, the $\mu^{1,1}_{F \Bar{F}}$ determines a deformation of the complex structure on $F$.
Furthermore, by Equation (\ref{eqn:gamma10}) we see that $\gamma^{1,0}$, hence $\beta = \partial \gamma^{1,0}$, is holomorphic for this deformed complex structure.
